COG-ED Manuscript

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
corrected typo (hyptohesis 3a vs 3b)
added caption of figure one to r chunk

```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}

@@

```
*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.

@@

@@

\endgroup

>>>>

```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back."}

@@

@@

Fit:
`r apa_print(hypothesis3b)$estimate$modelfit$r2`

@@
